\textbf{EECS 340: Assignment 7}

### 2020-04-27 assignment_7/article.tex
🔨 Add graph G setup description for Problem 1(a).
✨ Add Problem 2(a) response.

@@

>>>>

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(a)}

Set the each team as a node (vertex) in graph $G$ and make every node fully connected (representing the fact that all teams have played against each other). If one team $A$ beats another team $B$, we will have a directed edge of $A \rightarrow B$ betwen the nodes representing $A$ and $B$.

@@

Disprove with conterexample:

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{{fig/fig_2_a.png}}
\end{figure}

Note the tuple below each node represents their \ilc{(start-time, finish-time)}. It is shown that $v.f > u.f$ as $6 > 4$, however there is no circle between $uv$. Thus, this conterexample disproves the statement.
